---
title: "Midterm Project: General Mills"
author: "Akira Nakagawa, Anh Doan"
date: ""   
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
---

```{r}
#Course: BUAN 5210
#Purpose: Analyze effectiveness of Advertisement and Promotion, and comparison with competitors
#Date: 11/02/2019
#Author: Akira Nakagawa, Anh Doan
```

Preparing libraries and data for analysis
```{r message = FALSE}
# -- Clear environment of variables and functions------------------
rm(list = ls(all = TRUE)) 

# Clear environmet of packages
if(is.null(sessionInfo()$otherPkgs) == FALSE)lapply(paste("package:", names(sessionInfo()$otherPkgs), sep=""), detach, character.only = TRUE, unload = TRUE)

# -- Load packages ---------------------------------------
#install.packages("tidyverse") 
library(tidyverse)
# The gridExtra package contains grid.arrange function used to combine plots in the same window
library(gridExtra)
# The janitor package contains tidyverse functions for cross-tables
library(janitor)
# The knitr package contains some table formating functions
library(knitr)
# The GGally package contains a custom correlation plot we will use
library(GGally)
library(MultinomialCI)
library(htmlTable)
library(Hmisc)
library(formattable)
library(rms)
library(MultNonParam)


# -- Load data from mtp_data.csv -----------------------------------
mtp <- read.csv("mtp_data.csv")

# -- data cleansing  -----------------------------------
# Convert into factor variables
mtp$promo <- factor(mtp$promo)
mtp$iri_key <- factor(mtp$iri_key)

# Create a column for Company based on the column "brand"
Kell <- c("KELLOGGS COCOA KRISPIES", "KELLOGGS FROOT LOOPS", "KELLOGGS FROSTED MINI WHEATS", "KELLOGGS RAISIN BRAN", "KELLOGGS RICE KRISPIES", "KELLOGGS SMART START", "KELLOGGS SPECIAL K")
GM <- c("GENERAL MILLS CHEERIOS", "GENERAL MILLS CINNAMON TST CR", "GENERAL MILLS COCOA PUFFS", "GENERAL MILLS KIX", "GENERAL MILLS LUCKY CHARMS")
Po <- c("POST GRAPE NUTS", "POST SHREDDED WHEAT")
mtp <- transform(mtp, company= if_else( mtp$brand %in% Kell, "Kelloggs", if_else(mtp$brand %in% GM, "GM", "Post")))

```
<h2>Base EDA Step 1: Uni-variate non-graphical EDA</h2>
```{r message = FALSE, warning = FALSE}
# to look at the data 
head(mtp)
```
<h4>Comments</h4>
<div>
- In the price (per package), we can see only "0.5" in the first 6 rows. Need to investigate in further EDA steps.
- UPC is told to be a unique variable but it has duplications. 
</div>

```{r message = FALSE, warning = FALSE}
# to see how many observations, variables, types etc
str(mtp)
```
<h4>Comments</h4> 
<div>
- 5 Factor variables + promo(int)
    - Promo has to be factor based on the variable descriptions. We may need to be careful with this variable
    - UPC has 114 levels, which may be hard to show in visualization
    - Package only has 2 possible states: Box or Cup
- 4 continuous integer variables
- Assume iri-key and UPC are like a composite primary key
</div>

```{r message = FALSE, warning = FALSE}
summary(mtp)
```
<h4>Comments</h4> 
<div>
- Volume is symmetric. However, the max is 4.000, so we assume there are some outliers
- Price is symmetric. However, the min is 0.250 so we may have some outliars 
- week is told to be a time series
- Brand has information about producer and brands together, so it would be difficult to see the relation between the producers
- Because promo's 1st Qu, median, and 3rd Qu. are all 0. Thus, at least more than 75% of them do not have promotions
- Kelloggs sells the most out of three companies (What is the Kelloggs's strategy?)
</div>
<h4>Questions</h4>
<div>
- Is there significant difference of sales between promo and non-promo cereals?
- Is certain brand cheaper than the other?
- Is company/brand name an important factor for more sales?
- Is there significant difference between none-ad and with advertisement
</div>

<h2>Uni-variate graphical</h2>
<h3>Categorical</h3>

```{r message = FALSE, warning = FALSE}
grid.arrange(
# company
ggplot(data = mtp, mapping = aes(x = company)) +
  geom_bar(),
# brand
ggplot(data = mtp, mapping = aes(x = brand)) +
  geom_bar(),
# flavor
ggplot(data = mtp, mapping = aes(x = flavor)) +
  geom_bar(),
# package
ggplot(data = mtp, mapping = aes(x = package)) +
  geom_bar(),
# promo
ggplot(data = mtp, mapping = aes(x = promo)) +
  geom_bar(),
# ad
ggplot(data = mtp, mapping = aes(x = ad)) +
  geom_bar(),
ncol = 1 )
```
<h4>Comments</h4> 
<div>
- Most are Regular and Toasted (flavor)
- Most cereal package have no advertisement
- Company, Post, can be seen completing 2nd place in the market after GM
</div>

<h3>Quantative</h3>

<h4>Units</h4>
```{r message = FALSE, warning = FALSE}
grid.arrange(
# Create histogram
ggplot(data = mtp, mapping = aes(x = units)) + 
    geom_histogram(),

# Add boxplot
ggplot(data = mtp, mapping = aes(x = 1)) + 
    geom_boxplot(mapping = aes(y = units)) +
    coord_flip(), # use to have same x-axis on both graphs

# Set number of columns in grid.arrange
ncol = 1 )
```
<h4>Comments</h4> 
<div>
- Skewed
- Many rows have smaller units/sales
</div>

<h4>Volume</h4>
```{r message = FALSE, warning = FALSE}
grid.arrange(
# Create histogram
ggplot(data = mtp, mapping = aes(x = volume)) + 
    geom_histogram(),

# Add boxplot
ggplot(data = mtp, mapping = aes(x = 1)) + 
    geom_boxplot(mapping = aes(y = volume)) +
    coord_flip(), # use to have same x-axis on both graphs

# Set number of columns in grid.arrange
ncol = 1 )
```
<h4>Comments</h4> 
<div>
- Skewed
</div>

<h4>Price</h4>
```{r message = FALSE, warning = FALSE}
grid.arrange(
# Create histogram
ggplot(data = mtp, mapping = aes(x = price)) + 
    geom_histogram(),

# Add boxplot
ggplot(data = mtp, mapping = aes(x = 1)) + 
    geom_boxplot(mapping = aes(y = price)) +
    coord_flip(), # use to have same x-axis on both graphs

# Set number of columns in grid.arrange
ncol = 1 )
```
<h4>Comments</h4> 
<div>
- Symmetric
</div>

<h4>Questions</h4> 
<div>
- Why units's distribution is like this above.
</div>

<h2>Multi-variate non-graphical</h2>
<h3>Categorical</h3>
Company and Flavor
```{r message = FALSE, warning = FALSE}
# Company and Flavor
mtp %>% 
  tabyl(flavor, company) %>% # creates table of counts
  adorn_totals(where = c("row", "col")) # Total margins
```

```{r message = FALSE, warning = FALSE}
mtp %>% 
  tabyl(flavor, company) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>% # creates proportions
  adorn_rounding(2) # round decimals

```
<h4>Comments</h4> 
<div>
- Post sells only "Regular" flavor but they remarkably got 22% share in the cereal market.
- Only GM sells "Cinnamon flavor", and they got number one share in "cocoa flavor", but "cocoa" only has 9% of whole cereals...
- Other than "cinnamon and cocoa", GM is behind Kelloggs and Post
</div>
<br>

Package and brand(comapny)
```{r message = FALSE, warning = FALSE}
# package and brand
mtp %>% 
  tabyl(brand, package) %>% # creates table of counts
  adorn_totals(where = c("row", "col")) # Total margins
```
```{r message = FALSE, warning = FALSE}
mtp %>% 
  tabyl(brand, package) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>% # creates proportions
  adorn_rounding(2) # round decimals
```
Package and company
```{r message = FALSE, warning = FALSE}
# package and company
mtp %>% 
  tabyl(company, package) %>% # creates table of counts
  adorn_totals(where = c("row", "col")) # Total margins
```

```{r message = FALSE, warning = FALSE}
mtp %>% 
  tabyl(company, package) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>% # creates proportions
  adorn_rounding(2) # round decimals
```
<h4>Comments</h4> 
<div>
- Each company only sells 1% of cereal in a "CUP"
- Post has more "CUPs" relative to its sales size, Kelloggs has least CUPs in comparison with its "BOX"
</div>
<br>

Company and Ad
```{r message = FALSE, warning = FALSE}
# ad and company
mtp %>% 
  tabyl(company, ad) %>% # creates table of counts
  adorn_totals(where = c("row", "col")) # Total margins
```
```{r message = FALSE, warning = FALSE}
mtp %>% 
  tabyl(company, ad) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>% # creates proportions
  adorn_rounding(2) # round decimals
```
<h4>Comments</h4> 
<div>
- Kellogs put items on advertisement the most as whole and as proportion
  - Ratio for GM:       2:1:30 (9% has been advertised)
  - Ratio for Kelloggs: 3:2:39 (11% has been advertised)
  - Ratio for Post:     1:1:20 (9% has been advertised)
</div>
<br>

Company and Promo
```{r message = FALSE, warning = FALSE}
# promo and company
mtp %>% 
  tabyl(company, promo) %>% # creates table of counts
  adorn_totals(where = c("row", "col")) # Total margins
```

```{r message = FALSE, warning = FALSE}
mtp %>% 
  tabyl(company, promo) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all") %>% # creates proportions
  adorn_rounding(2) # round decimals
```
<h4>Comments</h4> 
<div>
- Kellogs put items on promo the most as a whole, Kellogs and Post work on promotion on the same propotion and greater than GM.
  - Ratio for GM:       27:6 (aprox.18% has been promoted)
  - Ratio for Kelloggs: 7:2 (aprox.22% has been advertised)
  - Ratio for Post:     17:5 (aprox.22% has been advertised)
</div>
<br>

<h3>Quantitative</h3>
```{r message = FALSE, warning = FALSE}
# Correlation table
mtp %>% 
  select_if(is.numeric) %>% # Use to select just the numeric variables
  cor() %>% 
  round(2) %>% 
  kable()
```
<h4>Comments</h4> 
<div>
- Price and volume has correlation
</div>
<h4>Question</h4> 
<div>
- Somehow units and price does not have correlation. Need to figure it out.
</div>
<br>

<h2>Multi-variate graphical</h4>
<h3>Categorical</h3>
```{r message = FALSE, warning = FALSE}
# More detail on promo,ad and company
grid.arrange(
  # ad and company
  mtp %>% 
    ggplot(mapping = aes(x = ad, fill = company)) + 
      geom_bar(position = "dodge"),
  # promo and company
  mtp %>% 
    ggplot(mapping = aes(x = promo , fill = company)) + 
      geom_bar(position = "dodge"),
  # flavor and company
  mtp %>% 
    ggplot(mapping = aes(x = flavor , fill = company)) + 
      geom_bar(position = "dodge"),
  # package and company
  mtp %>% 
    ggplot(mapping = aes(x = package , fill = company)) +
      geom_bar(position = "dodge"),
ncol = 1
)
```
```{r message = FALSE, warning = FALSE}
# More detail on company and ad
grid.arrange(
  mtp %>% 
    ggplot(mapping = aes(x = company, fill = ad)) + 
      geom_bar(position = "dodge") +
      coord_flip(),
  mtp %>% 
    ggplot(mapping = aes(x = company, fill = ad)) +
      geom_bar(position = "fill") +
      coord_flip(),
ncol = 1
)
```

```{r message = FALSE, warning = FALSE}
# More detail on brand and promo
grid.arrange(
    # Cluster of counts
  mtp %>% 
    ggplot(mapping = aes(x = company, fill = promo)) + 
      geom_bar(position = "dodge") +
      coord_flip(),
  # Proportion of counts
  mtp %>% 
    ggplot(mapping = aes(x = company, fill = promo)) +
      geom_bar(position = "fill") +
      coord_flip(),

ncol = 1
)
```
<h4>Comments</h4> 
<div>
- Confirm that GM has less advertisement and promo comparing with competitors
- Kellogs has more advertisement and promotion than the other
</div>

```{r message = FALSE, warning = FALSE}
mtp %>%
  group_by(ad, company) %>% 
  summarise(count = n()) %>% 
  ggplot(aes(ad, company)) + 
  geom_tile(aes(fill = count))
```
<h4>Comments</h4> 
<div>
- Kelloggs has slightly ligher color in A and B for ad. However, three company has almost the same pattern in advertisement.
</div>

<h3>Quantitative</h3>
```{r message = FALSE, warning = FALSE}
# price and units
mtp %>% 
  ggplot(mapping = aes(x = units, y = price)) +
  geom_point()

```
<h4>Comments</h4> 
<div>
- Price and units do not seem to have any relations.
</div>

```{r message = FALSE, warning = FALSE}
# volume and price
mtp %>% 
  ggplot(mapping = aes(x = volume, y = price)) +
  geom_point()
```
<h4>Comments</h4> 
<div>
- Price and volume seem to have relations/patterns.
</div>
<h4>Question</h4> 
<div>
- What does seperate between volume less than 0.5 and above? Advertisement or Promo?
</div>

```{r message = FALSE, warning = FALSE}
# volume and units
mtp %>% 
  ggplot(mapping = aes(x = volume, y = units)) +
  geom_point()
```
<h4>Comments</h4> 
<div>
- volume and units do not seem to have any relations.
</div>


<h3>Categorical and quantitative </h3>
```{r warning = FALSE, message = FALSE}

mtp %>%
  select(week, units, brand, flavor, package, volume, price, promo, ad, company) %>%
  ggpairs()
```
<h4>Comments</h4> 
<div>
- Look more closely at:
  - price and volume
  - price and flavor
  - volume and company
</div>
<br>
```{r message = FALSE, warning = FALSE}
# volume, price and company
mtp %>% 
    ggplot(mapping = aes(x = volume, y = price, color = company)) +
      geom_point() +
      geom_smooth(method = "lm", se = FALSE)
# volume, price and brand
mtp %>% 
    ggplot(mapping = aes(x = volume, y = price, color = brand)) +
      geom_point() +
      geom_smooth(method = "lm", se = FALSE)
  
# volume, price and flavor
mtp %>% 
    ggplot(mapping = aes(x = volume, y = price, color = flavor)) +
      geom_point() +
      geom_smooth(method = "lm", se = FALSE)

# volume, price and ad
mtp %>% 
    ggplot(mapping = aes(x = volume, y = price, color = ad)) +
      geom_point() +
      geom_smooth(method = "lm", se = FALSE)
```
<h4>Comments</h4> 
<div>
- Advertised has lower price on its similar volume
- GM's creal volume has more explanation to price than the other two companies'.
- Kelloggs have smaller range in terms of volume
</div>
```{r message = FALSE, warning = FALSE}
grid.arrange(
  # volume and flavor
  mtp %>% 
    ggplot(mapping = aes(x = flavor, y = volume)) +
      geom_boxplot(),
  # price nad flavor
  mtp %>% 
    ggplot(mapping = aes(x = flavor, y = price)) +
      geom_boxplot(),
    # price nad flavor
  mtp %>% 
    ggplot(mapping = aes(x = company, y = price)) +
      geom_boxplot(),
      # price nad flavor
  mtp %>% 
    ggplot(mapping = aes(x = company, y = units)) +
      geom_boxplot(),

ncol = 2
)
```
<h4>Comments</h4> 
<div>
- Advertised has lower price at sale on its similar volume
</div>
<h4>Questions</h4>
<div>
- We need to see the relation between Units and ad/promo of company
</div>
<br>
Units and company/ad
```{r message = FALSE, warning = FALSE}
mtp %>%
  group_by(ad, company) %>% 
  summarise(med_units = median(units)) %>% 
  ggplot(aes(ad, company)) +
  geom_tile(aes(fill = med_units))
```
<h4>Comments</h4> 
<div>
- GM's cereal with mediam advertisement has more sales/units than other
- However, because Kelloggs sells more, so we assume that Kelloggs has more power on its brand or there are more stores selling Kelloggs
</div>
<br>
Units and company/promo
```{r message = FALSE, warning = FALSE}
mtp %>%
  group_by(promo, company) %>% 
  summarise(med_units = median(units)) %>% 
  ggplot(aes(promo, company)) +
  geom_tile(aes(fill = med_units))
```
<h4>Comments</h4> 
<div>
- GM's cereal with promotion has the best sales/units than other
</div>
<br>

<h4>Questions</h4> 
<div>
- We need to see why GM has fewer units sold in total. 
</div>
<br>

<h2>Detailed EDA</h2>

Do units differ by promo, ads, or company(producer)
```{r message = FALSE, warning = FALSE}
# promo and units
mtp %>% 
  ggplot(mapping = aes(x = units)) +
  geom_histogram() +
  facet_wrap( ~ promo)
```
<div>
- Propotionally cereal with promotion are sold more units, especially for higher units
- Units without promotion have steep down but the units with promotion have less steepness
- Promotion may have influenced the number of units sold
</div>
```{r message = FALSE, warning = FALSE}
# ad and units
mtp %>% 
  ggplot(mapping = aes(x = units)) +
  geom_histogram() +
  facet_wrap( ~ ad)
```
<div>
- Pattern holds?
- Units without promotion have steep down but the units with promotion have less steepness
</div>

```{r message = FALSE, warning = FALSE}
# company and units
mtp %>% 
  ggplot(mapping = aes(x = units)) +
  geom_histogram() +
  facet_wrap( ~ company)
```
<h4>Comments</h4> 
<div>
- GM's cereal with promotion has the best sales/units than other
- Pattern holds
</div>
<br>


```{r message = FALSE, warning = FALSE}
mtp %>% 
    ggplot(mapping = aes(x = volume, y = units)) +
    geom_point() +
    geom_hline(yintercept = median(mtp$units), color="blue") +
    annotate(geom = "text", label = "units mean", x=3, y = 6, color="blue") +
    geom_smooth(mapping = aes(color = promo), method = "lm", se = FALSE)
```
<h4>Comments</h4> 
<div>
- if there is a promotion, there is more sales with volume
</div>
<br>

```{r message = FALSE, warning = FALSE}
mtp %>% 
    ggplot(mapping = aes(x = volume, y = units)) +
    geom_point() +
    geom_hline(yintercept = median(mtp$units), color="blue") +
    annotate(geom = "text", label = "units mean", x=3, y = 6, color="blue") +
    geom_smooth(mapping = aes(color = ad), method = "lm", se = FALSE)
```
<h4>Comments</h4> 
<div>
- both Ad A and B does not have points for heavier cereal product. We may need more information/data around there if possible
</div>
<br>

```{r message = FALSE, warning = FALSE}
mtp %>% 
    ggplot(mapping = aes(x = volume, y = units)) +
    geom_point() +
    geom_hline(yintercept = median(mtp$units), color="blue") +
    annotate(geom = "text", label = "units mean", x=3, y = 6, color="blue") +
    geom_smooth(mapping = aes(color = company), method = "lm", se = FALSE)
```
<h4>Comments</h4> 
<div>
- Company name does not have any relation with the units
</div>
<br>



<h2>Stats EDA</h2>
```{r}
#promo
(t <- t.test(mtp$units[mtp$promo == '1'], mtp$units[mtp$promo == '0'], conf.level = 0.95))
#ad
(t <- t.test(mtp$units[mtp$ad == 'B'], mtp$units[mtp$ad == 'NONE'], conf.level = 0.95))
```
<h4>Comments</h4> 
<div>
- reject the null hypothesis that the promotion does not impact the units/sales
</div>
<br>
```{r}
z <- qnorm(0.975) #95 percent

mtp %>%
  group_by(promo) %>%
  summarise(mn = mean(units), sd = sd(units), n = n(), ci = z * sd/sqrt(n)) %>%
  ggplot(aes(x = promo, y = mn)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = mn - ci, ymax = mn + ci), width = 0.5, position = position_dodge(0.9)) +
  labs(title = "Units/sales difference by Promotion with error bar")

mtp %>%
  group_by(ad) %>%
  summarise(mn = mean(units), sd = sd(units), n = n(), ci = z * sd/sqrt(n)) %>%
  ggplot(aes(x = ad, y = mn)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = mn - ci, ymax = mn + ci), width = 0.5, position = position_dodge(0.9)) +
  labs(title = "Units/sales difference by advertisement type with error bar")

```

Do brand/company units/sales vary based on promotion?
```{r}
chisq.test(table(mtp$brand, mtp$promo))
```
<h2>Comments</h2>
<div>
- X-square is large,so reject the null
- P-value is small, so reject the null
- According to the test,we cannot see what is different and what is similar
</div>
<br>

How do company units/sales vary with promotion
```{r}
C_P_n <- mtp %>%
  group_by(company, promo) %>%
  summarise(n = n())

C_P_n_ci <- multinomialCI(t(C_P_n[, 3]), 0.05)

C_P_tab <- mtp %>%
  group_by(company, promo) %>%
  summarise(prop = round(n()/sum(nrow(mtp)), 3))

C_P_tab$ci_l <- round(C_P_n_ci[,1], 3)
C_P_tab$ci_u <- round(C_P_n_ci[,2], 3)

htmlTable(C_P_tab)
```
```{r}
# Graph of proportions with confidence intervals
C_P_tab %>% 
  ggplot(aes(x = promo, y = prop, fill = company)) +
  geom_bar(stat="identity", position = "dodge") +
  geom_text(aes(label = round(prop, 2)), vjust = -4, color = "black", # vjust moves lables above CI
            position = position_dodge(0.9), size = 4) +
  geom_errorbar(aes(ymin = ci_l, ymax = ci_u), 
                width = 0.4, position = position_dodge(0.9)) +
  ggsave(filename = "support.png")
  
```




How do company units/sales vary with advertisement
```{r}
C_A_n <- mtp %>%
  group_by(company, ad) %>%
  summarise(n = n())
C_A_n_ci <- multinomialCI(t(C_A_n[, 3]), 0.05)

C_A_tab <- mtp %>%
  group_by(company, ad) %>%
  summarise(prop = round(n()/sum(nrow(mtp)), 3))

C_A_tab$ci_l <- round(C_A_n_ci[,1], 3)
C_A_tab$ci_u <- round(C_A_n_ci[,2], 3)

htmlTable(C_A_tab)
```
```{r}
# Graph of proportions with confidence intervals
C_A_tab %>% 
  ggplot(aes(x = ad, y = prop, fill = company)) +
  geom_bar(stat="identity", position = "dodge") +
  geom_text(aes(label = round(prop, 2)), vjust = -4, color = "black", # vjust moves lables above CI
            position = position_dodge(0.9), size = 4) +
  geom_errorbar(aes(ymin = ci_l, ymax = ci_u), 
                width = 0.4, position = position_dodge(0.9))
```
<h4>Comments</h4>
<div>
- Kelloggs has the most reliability in units/sales in any situation regardless if it has promotion or advertisement
</div>
<br>

Significance of Correlation
```{r}
mtp %>% 
  select_if(is.numeric) %>% 
  as.matrix() %>% 
  rcorr()
```

Multi-linear regression
```{r}
# Set up mtp data set for regression
mtp_lm <- mtp %>% 
  mutate_if(is.integer, as.factor)

# Logit regression with general linear model (glm)
mod <- glm(units ~ company + price + volume + flavor + package + promo + ad, 
           family = binomial(link='logit'), 
           data = mtp_lm)

# Review output
summary(mod)
```
<h4>Comments</h4>
<div>
- volume, flavorTOASTED, promo1 and adB are significant impact on units sold
</div>
<br>

```{r}
par(mfrow = c(1, 1))
# units
plot(mtp$units, mod$residuals)
```

```{r}
# company
plot(mtp$ad, mod$residuals)
```

```{r}
plot(mtp$volume, mod$residuals)
```
```{r}
# Flavor
plot(mtp$flavor, mod$residuals)
```
```{r}
# ad
plot(mtp$ad, mod$residuals)
```
```{r}
# promo
plot(mtp$promo, mod$residuals)
```
<div>
- units 
- Ad A and B are correlative but A has one outlier residuals
- units have residuals when unit is smaller
- some observed variable is far away from the regression. Threfore, we may need more variables and sample to run more accurate
</div>
<br>

Visualization of Multiple Regression
```{r}
coe <- summary(mod)$coefficients # get coefficients and related stats
coe_CI <- as.data.frame(cbind(coe[-1, ], confint(mod)[-1, ])) # find and bind CI, remove Intercept 

# Rename results data frame
names(coe_CI) <- c("estimate", "se", "t", "pval","low_CI","high_CI") 


# Order base on p-value
htmlTable(round(coe_CI[order(coe_CI$pval, decreasing = FALSE), ], 3))
```



```{r}
# reorder by p-value
(g1 <- ggplot(coe_CI, aes(x = estimate, y = reorder(row.names(coe_CI),desc(pval)))) +
  geom_point(size = 3) +
  xlim(min(coe_CI$low_CI), max(coe_CI$high_CI)) +
  ylab("Variable") +
  xlab("Coefficient") +
  theme_bw() 
)
```
<div>
- Volume has mroe the most significant impact on units/sales because its p-value is bigger than the alpha
- Variables with p-value less than alpha could be influencial on units/sales?
</div>
```{r}
# Use geom_segment to illustrate CI
(g2 <- g1 +
  geom_vline(xintercept = 0, color = "red")) +
  geom_segment(aes(yend = reorder(row.names(coe_CI),desc(pval))), 
               xend = coe_CI$high_CI, color = "Blue") +
  geom_segment(aes(yend = reorder(row.names(coe_CI),desc(coe_CI$pval))), 
               xend = coe_CI$low_CI, color = "Blue") +
  xlab("Coefficient with Confidence Interval") 
```
<div>
- 4 variables have positive p-value, which indicates positive outcome on units/sale.
  - volume
  - promo of 1
  - flavor toasted
  - ad of B
- variables with negative coefficient have negative impact on units/sales.
  - price
  - ad none
</div>


<h2>Summary</h2>
<div>
- Strategy:
  - Kelloggs has more advertisement, promotion (proportionally and quantatively), unit sales. 
  - Post has less unit sales but they are concentrated on a few products/brand
- What to recommend to GM
  - Promotion and advertisement are effective on unit sales 
</div>

<h2>Create professional quality graph</h2>
Graph for promo finding:
```{r message = FALSE, warning = FALSE}
z <- qnorm(0.975) #95 percent
levels(mtp$ad)[1] <- "Mediam Advertisement"
levels(mtp$ad)[2] <- "Small Advertisement"
levels(mtp$ad)[3] <- "No Advertisement"

levels(mtp$promo)[1] <- "Without Promotion"
levels(mtp$promo)[2] <- "With Promotion"

mtp %>%
  group_by(promo) %>%
  summarise(mn = mean(units), sd = sd(units), n = n(), ci = z * sd/sqrt(n)) %>%
  ggplot(aes(x = reorder(promo, mn) , y = mn)) +
  theme_classic() +
  geom_bar(stat = "identity", position = "dodge" ,fill = "light blue") +
  #geom_errorbar(aes(ymin = mn - ci, ymax = mn + ci), width = 0.5, position = position_dodge(0.9)) +
  labs(title = "Promotion has contributed more sales", subtitle = "Cereals with promotion have approximately 42% more sales",x = "", y ="Average weekly units sold", caption = "From Technical Appendix: Statistic EDA") +
  scale_y_continuous(breaks = seq(0, 16, 1)) +
  coord_flip() +
  ggsave(filename = "promo.png")

mtp %>%
  group_by(ad) %>%
  summarise(mn = mean(units), sd = sd(units), n = n(), ci = z * sd/sqrt(n)) %>%
  ggplot(aes(x = reorder(ad, mn) , y = mn)) +
  theme_classic() +
  geom_bar(stat = "identity", position = "dodge", fill = "light blue") +
  #geom_errorbar(aes(ymin = mn - ci, ymax = mn + ci), width = 0.5, position = position_dodge(0.9)) +
  labs(title = "Advertisement has an impact on our sales", subtitle = "Small advertisement have more impact on our sales than mediam advertisement", x = "", y = "Average weekly units sold", caption = "From Technical Appendix: Statistic EDA") +
  scale_y_continuous(breaks = seq(0, 16, 1)) +
  coord_flip() +
  ggsave(filename = "ad.png")
```




```{r}
(g1 <- ggplot(coe_CI, aes(x = estimate, y = reorder(row.names(coe_CI),desc(pval)))) +
  geom_point(size = 3) +
  xlim(min(coe_CI$low_CI), max(coe_CI$high_CI)) +
  ylab("Variable") +
  xlab("Coefficient") +
  theme_bw() +
  geom_vline(xintercept = 0, color = "red") +
  labs(title = "What customers makes customer buy more and buy less", subtitle = "Volume, Promotion, Flavor and Small ad have positive influence on sales", caption = "From Technical Appendix: Statistic EDA", x ="Unit Sale Influence level", y ="") +
  annotate(geom = "text", label = "Improves Unit sales", x=1, y = 1, color="dark blue") +
  annotate(geom = "text", label = "Decrease Unit sales", x=-0.7, y = 1, color="dark red") +
  theme_classic() +
  ggsave(filename = "coefficient.png")

)
```

